### 2020-08-20 5_evaluation.tex
Add paragraph for Chapel distrib in communication.

>>>>

The effectiveness of such overlap can be influenced by the scheduling
policies of the underlying system. For example, Chapel's default
scheduler uses a round-robin policy; we see in
Figure~\ref{fig:efficiency-communication} that this approach fails to
take full advantage of the available task parallelism. A work-stealing
scheduler (Chapel \lstinline{distrib}) is able to recover this
performance.
